Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-24 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
which is in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
However, restricting to $S^{2}$ enable us to visualize and imagine
easily. Also, if a interval-valued frame function~$\bar{f}$ has
an empty core when restricting to $S^{2}$, $\bar{\mu}$ has an empty
core on the original space as well. So restricting to $S^{2}$ still
provides valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
has an empty core. Furthermore, the larger the area, the more state
vectors which are inconsistent with any particular Born rule frame
function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
could indicate how much $\bar{f}$ deviate from the Born rule frame
functions.

>>>>

If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
which is in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
However, restricting to $S^{2}$ enable us to visualize and imagine
easily. Also, if a interval-valued frame function~$\bar{f}$ has
an empty core when restricting to $S^{2}$, $\bar{\mu}$ has an empty
core on the original space as well. So restricting to $S^{2}$ still
provides valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
has an empty core. Furthermore, the larger the area, the more state
vectors which are inconsistent with any particular Born rule frame
function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
could indicate how much $\bar{f}$ deviate from the Born rule frame
functions. In the following paragraphs, we will establish that if
the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ is big,
then the interval~$\mathscr{I}$ must be coarse. Therefore, if the
interval~$\mathscr{I}$ is finer, then the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
would be smaller so that $\bar{f}$ is closer to the frame function
derived from the Born rule.
